% ---------
%  Compile with "pdflatex hw0".
% --------
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{jeffe,handout,graphicx}
\usepackage[utf8]{inputenc}		% Allow some non-ASCII Unicode in source

%  Redefine suits
\usepackage{pifont}
\def\Spade{\text{\ding{171}}}
\def\Heart{\text{\textcolor{Red}{\ding{170}}}}
\def\Diamond{\text{\textcolor{Red}{\ding{169}}}}
\def\Club{\text{\ding{168}}}

\def\Cdot{\mathbin{\text{\normalfont \textbullet}}}
\def\Sym#1{\textbf{\texttt{\color{BrickRed}#1}}}
\usepackage{stmaryrd}


% =====================================================
%   Define common stuff for solution headers
% =====================================================
\Class{CS/ECE 374}
\Semester{}
\Authors{1}
\AuthorOne{Sushma Adari}{sadari2@illinois.edu}
%\Section{}

% =====================================================
\begin{document}

% ---------------------------------------------------------


\HomeworkHeader{0}{1}	% homework number, problem number
\Author{Sushma Adari}{sadari2}
\begin{quote}
\item 
Let $G=(V,E)$ be an undirected graph. Unless we say otherwise, a graph has no loops or parallel edges.

\begin{itemize}
\item Prove that if $|V| \ge 2$ there are two distinct nodes $u$ and $v$ such that degree of $u$ is equal to degree of $v$.  Recall that the degree of a node $x$ is the number of edges incident to $x$.
\item Prove that if $G$ has at least one edge then there is a path between two distinct nodes $u$ and $v$ such that degree of $u$ is equal to degree of $v$.
\end{itemize}

\end{quote}
\hrule



\begin{solution}
\item 
\begin{enumerate}[(a)]
\item The graph $G = (V,E)$ has a number of vertices $n \ge 2$, in the case where $n=2$ each distinct node $u$ and $v$ can either both have a degree of $1$ or a degree of $0$, since they can either be connected or unconnected. For every proceeding case the degree of the vertices in $G$, given $n$ nodes, can be any value between $0$ and $n-1$ since no loops or parallel edges exist in $G$. If $G$  has an arbitrary node, $A$, with degree $0$ none of the remaining nodes can have a degree of $n-1$ since it would require a shared edge with $A$. The remaining $n-1$ nodes' degrees can  be any value between 1 and n-2. And according to the pidgeon hole principle, at least $2$ of the remaining nodes $u$ and $v$ must have the same degree.

\item The graph $G = (V,E)$ has a number of edges $n$ where $n \ge 1$ and therefore by definition graph $G$ has a connected component that has at least two vertices. Applying the proof in part a to this connected component shows that there are at least 


\end{enumerate}
\end{solution}




% ---------------------------------------------------------
% Change authors for all future solutions
\HomeworkHeader{0}{2}
\AuthorOne{Sushma Adari}{sadari2}
\begin{quote}
\item The \EMPH{plus one}, $w^+$, of a string $w \in \set{\Sym0,\Sym1, \Sym2}^*$ is obtained from $w$ by replacing each symbol $a$ in $w$ by the symbol corresponding $a+1 \mod 3$. for example, $\Sym{0102101}^+ = \Sym{1210212}$.  The plus one function is formally defined as follows:
\[
	w^+ := \begin{cases}
		\e & \text{if $w=\e$}\\
		\Sym1\cdot x^+ & \text{if $w = \Sym0 x$}\\
		\Sym2\cdot x^+ & \text{if $w = \Sym1 x$} \\
		\Sym0\cdot x^+ & \text{if $w = \Sym2 x$}
	\end{cases}
\]

\begin{enumerate}
\item
{\bf Not to submit:} Prove by induction that $\abs{w} = \abs{w^+}$ for every string $w$.
\item
Prove by induction that $(x\Cdot y)^+ = x^+ \Cdot y^+$ for all strings 
$x, y \in  \set{\Sym0,\Sym1, \Sym2}^*$.
\end{enumerate}
Your proofs must be formal and self-contained, and they must invoke the \emph{formal} definitions of length $\abs{w}$, concatenation $x\Cdot y$, and 
plus one $w^+$.  Do not appeal to intuition!
\end{quote}
\hrule


\begin{solution}
\begin{quote}
\item
\textbf{Solution:} Let $x$ and $y$ be arbitrary strings and assume that for all strings $z$ ,where $|z| < |x|$, $(z\Cdot y)^+ = z^+ \Cdot y^+$ is true. 
\begin{enumerate}
\item
\textbf{Base Case:} Let $x$ be a string of length $0$. $x = \epsilon$
\begin{quote}
\item $(x\Cdot y)^+ =(\epsilon \Cdot y)^+ = (y)^+ = y^+$
\item $ = \epsilon \Cdot y^+ =  \epsilon ^+ \Cdot y^+ = x^+ \Cdot y^+$
\end{quote}
\end{enumerate}

\end{quote}
\end{solution}

% ---------------------------------------------------------

\HomeworkHeader{0}{3}

\begin{quote}
\newcommand{\bu}{\bf u}
\newcommand{\bv}{\bf v}
\item Let $\bu,\bv \in \R^2$ be two fixed vectors in the real plane.
Recursively define a set $L_n \subseteq \R^2$
as follows.
\begin{itemize}
\item $L_0 = \{\bu,\bv,{\bf 0}\}$. (${\bf 0}$ denotes the zero vector 
$(0,0)$ in $\R^2$.)
\item For integer $n > 0$, $L_n = \{ {\bf x}- {\bf y} \mid {\bf x}, {\bf y}
  \in L_{n-1} \}$.
\end{itemize}
Let $L = \bigcup_{n=0}^\infty L_n$. Also, let $D = \{ a{\bf u}+b{\bf
  v} \mid a,b \in \Z \}$ be the set of vectors obtained as integer
linear combinations of ${\bf u}$ and ${\bf v}$.
\begin{enumerate}
\item Prove that $D \subseteq L$, by giving, for each $a,b\in\Z$,
an explicit value of $n$ such that $a{\bf u}+b{\bf v}\in L_n$. 
(You don't need to
minimize the value of $n$; but you must argue why $a{\bf u}+b{\bf v} \in L_n$ for your
choice of $n$.)
\item Use mathematical induction to prove that for all integers $n\ge 0$,
$L_n \subseteq D$, and hence $L \subseteq D$.
\end{enumerate}
\end{quote}
\hrule


\begin{solution}[
\end{solution}

\end{document}